---
title: "Calendario Settimana"
output: html_document
---

<style>
  h1.title {
    display: none;
  }
</style>

Ultimo aggiornamento: `r format(now("CET"), "%d %B %Y %H:%M")`

```{=html}
<div style="display: flex; gap: 20px; font-family: Arial, sans-serif; font-size: 14px; font-weight: bold;">
  <p id="clock-bologna"></p>
  <p id="clock-cleveland"></p>
  <p id="clock-goodyear"></p>
</div>

<script>
  // Refresh page every hour (3600000 ms)
  setTimeout(function () {
    location.reload();
  }, 3600000);
  
  function getOffsetForTimeZone(timezone) {
    const now = new Date();
    const timeZoneDate = new Date(now.toLocaleString("en-US", { timeZone: timezone }));
    return timeZoneDate.getHours() - now.getUTCHours();
  }

  function updateClocks() {
    let now = new Date();

    let timeZones = {
      "clock-bologna": { name: "Bologna", offset: getOffsetForTimeZone("Europe/Rome") },
      "clock-cleveland": { name: "Cleveland", offset: getOffsetForTimeZone("America/New_York") },
      "clock-goodyear": { name: "Goodyear", offset: -7 } // Arizona stays at UTC-7
    };

    for (let id in timeZones) {
      let localTime = new Date(now.getTime() + timeZones[id].offset * 3600 * 1000);
      let hours = localTime.getUTCHours().toString().padStart(2, "0");
      let minutes = localTime.getUTCMinutes().toString().padStart(2, "0");
      
      document.getElementById(id).textContent = `${timeZones[id].name}: ${hours}:${minutes}`;
    }
  }
  
  setInterval(updateClocks, 1000);
  updateClocks(); // Run immediately on page load
setInterval(updateClock, 1000);
</script>
```

::: {#clock style="font-size: 24px; font-weight: bold;"}
:::

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
```

##  {.tabset}

### Corrente

```{r, echo=FALSE, ft.arraystretch = 1}
set_flextable_defaults(fonts_ignore=TRUE)
tables[[1]]

```

### Prossima

```{r, echo=FALSE, ft.arraystretch = 1}

tables[[2]]

```

## Note

<canvas id="drawingCanvas" width="400" height="300" 
        style="border:2px solid black; touch-action: none;"></canvas>
<br>
<button onclick="clearCanvas()">Clear</button>

<script>
  var canvas = document.getElementById("drawingCanvas");
  var ctx = canvas.getContext("2d");
  var drawing = false;

  function getMousePos(event) {
    var rect = canvas.getBoundingClientRect();
    return {
      x: event.clientX - rect.left,
      y: event.clientY - rect.top
    };
  }

  function startDraw(event) {
    drawing = true;
    var pos = getMousePos(event);
    ctx.beginPath();
    ctx.moveTo(pos.x, pos.y);
    event.preventDefault();
  }

  function draw(event) {
    if (!drawing) return;
    var pos = getMousePos(event);
    ctx.lineTo(pos.x, pos.y);
    ctx.strokeStyle = "black"; 
    ctx.lineWidth = 2;
    ctx.stroke();
    event.preventDefault();
    saveCanvas(); // Save after each stroke
  }

  function stopDraw() {
    drawing = false;
    ctx.closePath();
    saveCanvas(); // Save final drawing state
  }

  function clearCanvas() {
    ctx.clearRect(0, 0, canvas.width, canvas.height);
    localStorage.removeItem("savedCanvas"); // Remove saved data
  }

  function saveCanvas() {
    localStorage.setItem("savedCanvas", canvas.toDataURL()); // Convert canvas to an image string
  }

  function loadCanvas() {
    var savedData = localStorage.getItem("savedCanvas");
    if (savedData) {
      var img = new Image();
      img.onload = function () {
        ctx.drawImage(img, 0, 0);
      };
      img.src = savedData;
    }
  }

  // Load canvas on page load
  window.onload = loadCanvas;

  // Mouse Events
  canvas.addEventListener("mousedown", startDraw);
  canvas.addEventListener("mousemove", draw);
  canvas.addEventListener("mouseup", stopDraw);
  canvas.addEventListener("mouseout", stopDraw);

  // Touch Events (for stylus or touchscreen)
  canvas.addEventListener("touchstart", function(event) {
    startDraw(event.touches[0]);
  });

  canvas.addEventListener("touchmove", function(event) {
    draw(event.touches[0]);
  });

  canvas.addEventListener("touchend", stopDraw);
</script>